%*******************************************************
% Acknowledgements
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{Acknowledgements}

\begin{flushright}{\slshape    
		In general, the remote sensing problem \\
		can be presented as inferring the order \\ 
		in the properties and distributions of matter \\ 
		and energy in the scene from the set \\
		of measurements comprising the image.} \\ \medskip
%		--- \defcitealias{Strahler:1986}{Alan H. Strahler et al. 1986}\citetalias{Strahler:1986} \citep{Strahler.1986}
		--- \cite{Strahler.1986}
		
	
\end{flushright}


\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}

I would like to take the opportunity to thank all those involved in the work I did in the last years.
Without your help and support, I would not have been able to mastering the challenges on my way to this thesis.

First of all, I express my gratitude to Prof.\,Dr.\,Hans Pretzsch, 
who complied to supervise me as external Ph.D. Student at Technische Universität München. 
He always encouraged me to pursue on my objectives and supported me with his great experience in scientific work.
His different perspective to my work, underpinned by his enormous knowledge in forest growth and yield, added great value to my research; 
our meetings often resulted in very fruitful discussions developing new ideas and hypotheses.

I am thankful to Prof.\,Dr.\,Thomas Knoke for his willingness to act as second examiner
and to Prof.\,Dr.\,Stephan Pauleit for taking over the chair of the committee.
Many thanks go to Prof.\,Dr.\,Clement Atzberger from the University of Natural Resources and Life Sciences 
for agreeing to examine this thesis, but much more for many helpful discussions and advises.  

I am very thankful to Dr.\,Christoph Straub. 
You have been a great colleague, a perfect partner and an ongoing supporter.
I enjoyed it very much collaborating with you. 
Many thanks also go to Rudolf Seitz for giving me the opportunity to work in this project, 
to Helena Löffler, Kristine Meyerhofer, and Oliver Bauer for sharing their ideas, skills and coffee breaks,
and all my colleagues at the \myInstitute. 
A special thanks goes to Michael Suda for running together criss-cross around Freising.
Not only the sports, but also our conversations did me good.   
 
I am very grateful to Markus Immitzer for his invaluable aid during working on different aspects of this thesis. 
Thanks for sharing your knowledge in the \textsf{R} programming language, 
for very in-depth discussions and constructive feedback, 
and for the possibility to co-author a terrific paper.    

I owe special thanks to Joanne White, Mike Wulder (Canadian Forest Service),
Nicholas Coops, Piotr Tompalski (Integrated Remote Sensing Studio, UBC) and the complete crowd of IRSS for giving me the chance to work abroad in a very inspiring team. 
You made one of the best experiences during my Ph.D. possible. 
I am also very thankful to Brynn McMillan for sharing a great time in Vancouver. 

\noindent Finally, many thanks to \emph{Melanie}. You always believed in me. I'm so happy that you're with me.

\endgroup



