%*******************************************************
% Acknowledgements
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{Acknowledgements}

\begin{flushright}{\slshape    
		In general, the remote sensing problem \\
		can be presented as inferring the order \\ 
		in the properties and distributions of matter \\ 
		and energy in the scene from the set \\
		of measurements comprising the image.} \\ \medskip
	--- \defcitealias{Strahler:1986}{Alan H. Strahler et al. 1986}\citetalias{Strahler:1986} \citep{Strahler.1986}
\end{flushright}


\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}

I would like to take the opportunity to thank all those involved in the work I did in the last years. Without your help and support, I would not have been able to mastering the challenges on my way to this thesis.

First of all, I express my gratitude to Prof. Dr. Hans Pretzsch, who complied to supervise me as external PhD Student at Technische Universität München. He ...

I gratefully acknowledge \dots
I am furthermore thankful to \dots
Many thanks go to \dots

I thank all my colleagues at the LWF, in particular ..., 

for their invaluable aid during working on the different aspects of this thesis. 
... the precision in the suggestions, the good advices.

\emph{Personensammlung:}

\begin{itemize}
	\item Prof. Dr. Thomas Knoke für die Übernahme der Zweitkorrektur
	\item Prof. Dr. Stephan Pauleit für den Vorsitz der Prüfungskommision
	\item Prof. Dr. Clement Atzberger für die Übernahme der Zweitkorrektur und viele hilfreiche Hinweise und Diskussionen
	\item Dr. Christoph Straub
	\item Rudolf Seitz
	\item Helena Löffler, Kristine Meyerhofer, Oliver Bauer and the other colleagues at LWF
	\item Michael Suda fürs Laufen
	\item Markus Immitzer
	\item Lars Waser
	\item Joanne White and Mike Wulder
	\item Nicholas Coops and Piotr Tompalski plus the complete crowd of IRSS
	\item Brynn McMillan for sharing a great time in Vancouver
	\item Laura Carlson for language editing
	\item \dots
\end{itemize}

\noindent Finally, thanks to \emph{Melanie}. You always believed in me. I'm so happy that you're with me.

\endgroup



